---
title: "Getting started with texanshootR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with texanshootR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  eval     = FALSE
)
```

`texanshootR` provides a structured, terminal-first interface for
exploratory linear-model search. The main entry point is `shoot()`.

## A first run

```{r}
library(texanshootR)

run <- shoot(mtcars)
print(run)
summary(run)
```

The returned `tx_run` object stores the highlighted specification, the
search summary, and any life events that fired during the run.

## The career

The package keeps a persistent career across runs in
`tools::R_user_dir("texanshootR", "data")`. Use `career()` to see your
current state:

```{r}
career()
```

The first time you save, you'll be prompted to confirm the path. Set
`options(texanshootR.save_enabled = FALSE)` to opt out entirely.

## Unlocks

Only `shoot()` and the inspection helpers are callable from session
one. The six output generators are gated by career tier and unlock as
the career advances. `progress()` prints the live lock map:

```{r}
progress()
```

The tier-to-function mapping:

| Tier              | Unlocks                                                    |
|-------------------|------------------------------------------------------------|
| Junior Researcher | `shoot()`, `career()`, `achievements()`, `wardrobe()`, `run_log()`, `progress()`, resets |
| Postdoc           | `manuscript()`                                             |
| Senior Scientist  | `reviewer_response()`, `graphical_abstract()`, `presentation()` |
| PI                | `funding()`                                                |

A locked call signals a `tx_locked` condition with a two-block status
message. From a fresh save:

```
manuscript() requires:
Postdoc

Current career:
Junior Researcher
```

Scripts can intercept the signal with
`tryCatch(manuscript(run), tx_locked = function(c) NULL)`. Inspect a
single function's status with `progress("manuscript")`. Tier
thresholds are not documented; the path is more runs.

## Output generators

Each output function takes a `tx_run` and writes to `tempdir()` by
default. Override with `output_dir` or
`options(texanshootR.output_dir = ...)`. Once the relevant tier is
reached, the call works the same way for every generator:

```{r}
manuscript(run)
reviewer_response(run)
graphical_abstract(run)
presentation(run)
funding(run)
```

Output functions return the file path invisibly and print a short
status line.

## Achievements and cosmetics

```{r}
achievements()
wardrobe()
```

Hidden achievements appear as `???` until unlocked. New cosmetics
auto-equip when their unlocking achievement fires; override the
selection with `wardrobe(slot, id)`.

## Resetting

If you want to start over:

```{r}
reset_career(force = TRUE)
reset_all(force = TRUE)
```
